---
title: "Project: Example for Class"
format: html
execute: 
  echo: false
  warning: false
  message: false
embed-resources: true
---


```{r}
#| label: setup
#| include: false
library(tidyverse)
```


## Data Description

Here is a description of my data and a link to the source embded here with references.  



## Data Cleaning  

Here I describe in plain speak what I did to clean the data.  Do not show code or use technical terms.  I want to be able to read this and understand what I did.  


```{r}
#| label: data-cleaning
#this shoud be hidden from view and no seen in the website it shoudl include your data cleaning and you should export the clean data

```

```{r}
#| label: read-data
#read in your clean data here
```


## Visualzation 1
Here is a description of the first visualization.  I want to describe what the visualization shows to a general audience.  I do not want to see any code or technical terms.  I want to be able to read this and understand what the visualization shows.  I also want to see a caption and alt text for the visualization.  The caption should be a short description of the visualization and the alt text should be a longer description of the visualization.  The alt text should be descriptive enough that someone who is blind could understand what the visualization shows.

```{r}
#| label: viz-1
#| fig-cap: "This is a caption for the first visualization"
#| fig-alt: "This is an alternative text for the first visualization"
#| fig-width: 6
#| fig-height: 4
#| fig-align: center

#create plot of iris dataset
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point() +
  labs(title = "Iris Dataset", 
       x = "Sepal Length", 
       y = "Sepal Width") +
  theme_minimal()
```



## Visualization 2
Here is a description of the second visualization.  I want to describe what the visualization shows to a general audience.  I do not want to see any code or technical terms.  I want to be able to read this and understand what the visualization shows.  I also want to see a caption and alt text for the visualization.  The caption should be a short description of the visualization and the alt text should be a longer description of the visualization.  The alt text should be descriptive enough that someone who is blind could understand what the visualization shows.

```{r}
#| label: viz-2
#| fig-cap: "This is a caption for the second visualization"
#| fig-alt: "This is an alternative text for the second visualization"
#| fig-width: 6
#| fig-height: 4
#| fig-align: center

#create plot of cars data set
ggplot(cars, aes(x = speed, y = dist)) +
  geom_point() +
  labs(title = "Cars Dataset", 
       x = "Speed", 
       y = "Distance") +
  theme_minimal()
```
